### 2023-03-20 paper-reviews/papers-2023.tex
Add scalar waving paper

>>>>

\section*{GPU}
\begin{itemize}
    \item \cite{Yilmazer:ScalarWaving:2014}:

    The authors discovered that GPU programs contain significant portion of scalar instructions. 30\% for the GPU selected benchmarks in the paper. The papers states that scalar instructions are typically executed as SIMD with all vector elements having the same values. Thus, the same computation is performed redundantly. One of the solution for the problem is to run the calculations once and than broadcast the results in order to reduce power consumption on unnecessary operations. The authors suggested to statically detect scalar operations during compilations. One negative effect of this is reduced utilization of SIMD lanes. To improve utilization the  paper proposed scalar waving --- grouping of same scalar instructions processing different scalars into a single SIMD instruction. This grouping is suggest to be performed during runtime through by GPU itself. Further, the authors developed simultaneous scalar and SIMD group waving --- grouping and a SIMD instructions and scalar ware. GPU needs to be able to execute two different operations as a part of SIMD instruction in this case. The authors claim to achieve up to 25\% percent performance improvement for the selected benchmarks. The performance studies are performed on \href{https://github.com/gpgpu-sim}{GPGPU-Sim} simulator.
\end{itemize}
